\section{Metrics \& Experimental Setup}

\subsection{Multi-Dimensional Metrics}

\evobench{} defines three primary outcome metrics and a set of process metrics:

\textbf{Outcome metrics.}
\begin{itemize}[nosep]
\item \emph{Mean Reward (MR)}: weighted average of task scores with resurrection bonus:
\[
\text{MR} = \frac{\sum_{i=0}^{5} s_i \cdot w_i \cdot b_i}{\sum_{i=0}^{5} w_i \cdot b_i}
\]
where $s_i$ is the score for Task~$i$, $w_i = [0.05, 0.20, 0.20, 0.15, 0.30, 0.10]$ are task weights reflecting the increasing difficulty and importance of IR optimization (Task~4), and $b_i = 1.2$ if Task~$i$ was \emph{not} resurrected (rewarding independent success) or $b_i = 1.0$ if resurrected.

\item \emph{Pass Score (PS)}: weighted pass rate with resurrection penalty:
\[
\text{PS} = \frac{\sum_{i=0}^{5} p_i \cdot b_i^{\text{pass}}}{6 \times 1.5} \times 100
\]
where $p_i = 1$ if $s_i \geq 60$ else $0$, and $b_i^{\text{pass}} = 1.5$ if not resurrected, $1.0$ if resurrected.

\item \emph{Pipeline Score (PL)}: simple average of task scores: $\text{PL} = \frac{1}{6}\sum_{i=0}^{5} s_i$.
\end{itemize}

\textbf{Process metrics.}
Beyond outcome scores, we record token consumption (input/output), interaction turns, command executions (shell/build/test), retry counts, elapsed wall-clock time, and failure type (categorized into five types: predecessor failure, task-local reasoning failure, execution failure, process collapse, cost overrun).

\textbf{Failure taxonomy.}
We categorize agent failures into five types:
(1)~\emph{predecessor failure}---downstream unreachable due to missing artifact;
(2)~\emph{task-local reasoning failure}---cannot solve despite correct prerequisites;
(3)~\emph{execution failure}---build/dependency errors;
(4)~\emph{process collapse}---max-turn exhaustion, search loops;
(5)~\emph{cost overrun}---budget exhausted.

\subsection{Models and Agent Backends}

We evaluate \evobench{} across 22 model configurations spanning both proprietary and open-weight LLMs, using four agent backends:

\begin{table}[t]
\centering
\small
\begin{tabular}{lll}
\toprule
\textbf{Backend} & \textbf{Type} & \textbf{Key Properties} \\
\midrule
OpenHands SDK & Full agent framework & Unlimited self-loop, skill injection, MCP \\
Codex CLI & CLI agent & Autonomous coding with sandboxed execution \\
Claude Code & CLI agent & File I/O, command execution, multi-turn \\
Kimi CLI & CLI agent & Conversational coding with plan management \\
\bottomrule
\end{tabular}
\caption{Agent backends used in \evobench{} evaluation.}
\label{tab:backends}
\end{table}

\subsection{Evaluation Settings}

We conduct evaluation under two primary settings:

\textbf{Setting~1: Serial pipeline with resurrection (default).}
Agents proceed through Tasks~0--5 in sequence.
When a task fails, resurrection is triggered and the agent continues with the golden intermediate artifact.
This setting produces the full leaderboard with both outcome and process metrics.

\textbf{Setting~2: Serial pipeline without resurrection.}
Agents proceed through Tasks~0--5 in sequence, but \emph{no resurrection is triggered}.
When a task fails, all subsequent tasks receive the agent's (possibly broken) artifact and typically cascade to zero scores.
This setting measures \emph{zero-shot pipeline depth}.

The comparison between Setting~1 and Setting~2 directly tests whether resurrection recovers diagnostic signal lost to cascading failure.

\subsection{Workload Comparison: \yatcc{} vs. \yatcc{}-Hard}

We evaluate models on both workloads to quantify the difficulty gap between scaffolded and from-scratch implementation.
\yatcc{} provides starter code and implementation frameworks; \yatcc{}-Hard removes all code logic, requiring agents to construct the full compiler from minimal specification.
The performance delta between the two workloads measures the value of scaffolding and reveals which models depend on provided structure versus which can operate autonomously.