\section{Introduction}

Large language models have rapidly evolved from conversational assistants into autonomous software engineering agents capable of planning, implementing, debugging, and deploying complex infrastructure stacks~\cite{jimenez2024swebench,liu2024agentbench,frontiereng2026}.
Modern agentic development frameworks demonstrate increasingly sophisticated capabilities in repository-level code generation, multi-file reasoning, and tool orchestration.
Yet the evaluation methodologies for these systems remain rooted in a \emph{benchmark-driven paradigm}: isolated, static, short-horizon tasks where each evaluation unit is independent and the agent is reset after every attempt.

This paradigm has a fundamental limitation: \emph{real production engineering is not a collection of independent tasks}.
In practice, production infrastructure engineering involves long-horizon iterative development, multi-file and cross-module reasoning, dependency management, runtime debugging, tool orchestration, deployment validation, continuous integration pipelines, environment instability, resource constraints, and recovery from cascading failures.
Static benchmarks cannot capture these dynamics---they measure instantaneous coding ability, not engineering evolution.

\textbf{The gap.}
As a result, strong benchmark performance does not necessarily imply practical engineering utility.
Models optimized for benchmark-style coding may still fail in realistic production environments where runtime correctness, execution robustness, and adaptive recovery become critical.
We argue that the field needs to move \emph{beyond benchmarks} toward \emph{evaluation frameworks}---systems that assess agentic models in realistic, multi-stage production environments with controlled intermediate state injection, multi-dimensional metrics, and systematic failure diagnosis.

\textbf{Our approach.}
We present \eva{} (Evaluating Agentic Models in Production Systems), a production-grounded evaluation framework built upon the \yatcc{} integrated platform.
\eva{} provides a unified evaluation architecture supporting heterogeneous LLM providers and agent SDKs (OpenHands, Claude Code, Codex CLI, Kimi CLI) through standardized API access via \textsc{AIhub}.
It features realistic long-horizon compiler construction workloads organized as serial dependency chains with two difficulty levels (\yatcc{} and \yatcc{}-Hard), a \resurrection{} mechanism that decomposes cascading failure into diagnostic components, and utility-oriented multi-dimensional metrics measuring both outcome quality and process efficiency.

Our contributions are:
\begin{enumerate}[nosep]
\item We propose \eva{} as a production-grounded evaluation \emph{framework} (not a benchmark) that moves beyond synthetic, isolated task evaluation toward persistent, runtime-observable, production-grounded assessment of agentic models.
\item We design realistic long-horizon engineering workloads with strict serial dependencies and verifiable intermediate states, spanning two difficulty levels that quantify the value of scaffolding in agentic coding tasks.
\item We introduce a unified evaluation architecture and utility-oriented metrics that support heterogeneous LLMs and agent frameworks, measuring not just outcome scores but process cost, failure patterns, and deployment-relevant efficiency.
\item We provide empirical evidence across 22 model configurations, four agent backends, and two workload difficulty levels, demonstrating that serial evaluation reveals failure patterns invisible to static benchmarks and that resurrection recovers substantial downstream diagnostic signal.
\end{enumerate}